An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-24 comment.tex
worsd

\section{Results}\label{section:results}
We plot $\err{exact}$ for varying prevalence $q$ and sensitivity $\Se$
values, and make the comparison with $\err{common}$. As recommended by
\cite{DorfmanYuvalDor}, we apply different pool sizes $N$, for
different prevalence values. We observe that for a false-positive rate
$\Sp=0.95$ \cite{DorfmanYuvalDor} and a range of reasonable
sensitivity and prevalence values \cite{KitComparison,
  InterpretingCOVID19Test, EstimatingRatesLourenco,
  FalsePositiveEstimate}, an increase of at least $60\%$ in
$\err{exact}$ can be expected (Figure \ref{figy}).

>>>>

\section{Results}\label{section:results}
\subsection{Scheme false-negative}
We plot $\err{exact}$ for varying prevalence $q$ and sensitivity $\Se$
values, and make the comparison with $\err{common}$. As recommended by
\cite{DorfmanYuvalDor}, we apply different pool sizes $N$, for
different prevalence values. We observe that for a false-positive rate
$\Sp=0.95$ \cite{DorfmanYuvalDor} and a range of reasonable
sensitivity and prevalence values \cite{KitComparison,
  InterpretingCOVID19Test, EstimatingRatesLourenco,
  FalsePositiveEstimate}, an increase of at least $60\%$ in
$\err{exact}$ can be expected (Figure \ref{figy}).
